Mahotas: Open source software for scriptable computer vision

### 2013-04-24 paper.tex
BUG Fix code bug in paper
Pointed out by reviewers

Finally, we can show the points in different colours.
\begin{python}
colors = np.array(
    [ 255,  25,   1],
    [203,  77,  37],
    [151, 129,  56],
    [ 99, 181,  52],
    [ 47, 233,   5]])
f2 = surf.show_surf(f, spoints[:64], values, colors)
\end{python}

>>>>

Finally, we can show the points in different colours.
\begin{python}
colors = np.array([
    [ 255,  25,   1],
    [203,  77,  37],
    [151, 129,  56],
    [ 99, 181,  52],
    [ 47, 233,   5]])
f2 = surf.show_surf(f, spoints[:64], values, colors)
\end{python}
